%!TEX root = mainfile.tex

\newpage
\section{Rate of Re-ionizing photons} % (fold)
\label{sec:rate_of_reionizing_photons}
	With a knowledge of the luminosity density, it is possible to calculate the star formation rate density, using the following formula.
	\begin{align}
		\rho_{SFR} &= 1\times 10^{-28}\rho_L \label{eq:star_form_rate}
	\end{align}
	Using estimates of the fractional escape and zeta, we can use equation~(\ref{eq:star_form_rate}) to calculate the rate of reionization. From this, and the number of neutral hydrogen particles in the universe, it is possible to calculate the timescale of reionization.
	\begin{align}
	t =\frac{dNion}\d{t}\times \frac{1}{N_H}
	\end{align}
	Where t is the time between the start of reionization and the end, in seconds, Nion is the number of ionizing photons produced and $N_H$ is the number of hydrogen atoms in the universe.

	As the number of photons produced roughly equalls the number of neutral hydrogen in the universe, it is possible to calculate a limit on the redshift accosiated with the end of reionization, given the corresponding opposite limit.

	A simulation of this was undergone using the equation above, and the resultant timescale was found to be\ldots

	\subsection{Techniques for Finding an Upper Limit on Redshift} % (fold)
	\label{sub:techniques_for_finding_an_upper_limit_on_redshift}
		We know that when $\rho_{SFR}$ and $\rho_{SFR}*$ are equal, reionization will begin. Knowing the Clumping factor (See Section~\ref{sec:clumping_factor}) it is possible to calculate the critical Star formation rate density, using the following equation,
		\begin{align}
		\rho_{SFR}*=2\times 10^3\frac{C}{f_{esc}} {\left( \frac{1+z}{10} \right )}^3
		\end{align}
		Where $f_{esc}$ is the fractional escape of photons from reionizing spheres, and C is the clumping factor. Combining with equation X it is possible to calculate the conditions for which reionization began as follows:
		\begin{align}
		1\times10^{-28}\int^{\infty}_{L}L\phi(L) dL=2\times 10^3\frac{C}{f_{esc}}{\left( \frac{1+z}{10} \right)}^3
		\end{align}
		Solving this equation, will give an upper $z$ limit to reionization, and using the timescale in Section~\ref{sec:rate_of_reionizing_photons} it is possible to calculate both limits.

		The resultant values for redshift were z+/-z
	% subsection techniques_for_finding_an_upper_limit_on_redshift (end)

	\subsection{Jeans Mass for Collapse and Galaxy Formation} % (fold)
	\label{sub:jeans_mass_for_collapse_and_galaxy_formation}
		The Jeans Mass defines the cirtical mass of a cloud before it can collapse to form a galaxy, thereby limiting the minimum mass of a star foming galaxy. It is defined as the equation below:
		%\begin{align}
		%M_J=\left ( \frac{5kT}{Gm}\right ) ^{3/2} \left ( \frac{3}{4\pi\rho} \right ) ^{1/2}
		%\end{align}
		\begin{align}
			M_J = 5.73\times 10^3{\left(\frac{\Omega_m h}{0.15} \right)}^{-1/2} {\left( \frac{\Omega_b h^2}{0.022}\right)}^{-3/5} {\left( \frac{1+z}{10} \right)}^{3/2} M_\odot
		\end{align}
		Assuming an appropriate Mass-Luminosity ratio, this corresponds to an upper limit on both the Luminosity and the Absolute Magnitude (i.e.\ the dimmest ionizing galaxy.) This therefore provides a lower limit of magnitude to the Schechter function, the L specified in the equation in the previous section
	% subsection jeans_mass_for_collapse_and_galaxy_formation (end)

	\subsection{Mass-Luminosity Ratios} % (fold)
	\label{sub:mass_luminosity_ratios}
		An appropriate Mass-Luminosity Formula is:
		\begin{align}
			L(M) = L_0 \times \frac{{(M/M_s)}^a}{q+{(M/M_s)}^{cd}}^{1/d}
		\end{align}
		where $d=0.23$, $a=40$, $q=0.57$ and $c=3.57$. Or you can get the star formation rate of a galaxy from the mass (0911.1356v4) and from this you can obtain the Magnitude Kennicutt 1998 conversion from UV luminosity to AB magnitude and thereby to luminosity.
	% subsection mass_luminosity_ratios (end)

	% \subsection{Press Schechter Formalism} % (fold)
	% \label{sub:press_schechter_formalism}
	% 	PSF is a method of obtaining the number of objects with a specific mass within a certain volume. It assumes that the universe linearly ``clumped'' at the beginning of the universe, until a point where the density of the clumps break away from the rest of the universal expansion, and is treated as a massive body which collapses rapidly. (this occurs at around $\delta_c$\~1.68- Gunn and Gott). Press and Schechter suggest a probability distribution function of =:
	% 	\begin{align}
	% 	p(M,z)=-2p_0 \frac{\Delta P [\delta_v>\delta_c(z)]} {\Delta M} dM
	% 	\end{align}
	% 	Where $p_0$ is the mean density of the universe, and $\delta_c(z)$ is the overdensity threshold per redshift. P is the cumulative probability distribution of $\delta_v$ (volume)

	% 	It is from this that Schechter functions of luminosity and magnitude could arise\ldots
	% % subsection press_schechter_formalism (end)

% section rate_of_reionizing_photons (end)
